Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Typo.

All that remains is the interpretation of primitives.  For abstract
intepretation, we set $\interpdelta$ to the function that returns
$\sNum$ on all inputs---a symbolic value we interpret as denote the
set of all integers.

>>>>

All that remains is the interpretation of primitives.  For abstract
intepretation, we set $\interpdelta$ to the function that returns
$\sNum$ on all inputs---a symbolic value we interpret as denoting the
set of all integers.
